Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS

### 2023-08-15 paper/ms.tex
updated planet paragraph based on feedback from Saul

\subsection{Constraints on the presence of a planet}
\label{subsec:planet_constraints}
We searched for evidence of a transiting exoplanet for 10 of the brightest
CQVs {\red (RJ: was this the selection function?)} using the transit least
squares algorithm from \citet{2019A&A...623A..39H}. We first fit for 40
harmonics of the CQV period and subtracted these from the light curve,
along with two sidebands at frequencies of $1/T$, where $T$ was the
length of the TESS data for the sector whose data we used. We found
no evidence for a planet with $R > 2-3 R_\oplus$ and a period less
than 12\,d (FAP > 0.05) in most cases. The three false positive cases
could be explained by residual signals from the CQV that were not
properly removed, due to the modulation of the CQV profile over
the duration of a period. Further observations may be necessary to
conclusively rule out the presence of planets around CQVs.

>>>>

\subsection{Constraints on the presence of a planet}
\label{subsec:planet_constraints}
We searched for evidence of a transiting exoplanet for 10 of the brightest
CQVs {\red (RJ: was this the selection function?)} using the transit least
squares algorithm from \citet{2019A&A...623A..39H}. We first fit simultaneously
for 30 harmonics of the CQV period, along with $\pm$\,3 sidebands of each
harmonic spaced by $1/T$, where $T$ was the duration of the TESS
data for the sector we used. This fit, using 420 frequencies, was then subtracted 
from the TESS light curve, and we then analyzed the residual. We found
no evidence for a planet with $R > 2-3 R_\oplus$ and a period less
than 12\,d (FAP > 0.05) in most cases. The three false positive cases
could be explained by residual signals from the CQV that were not
properly removed, due to the modulation of the CQV profile over
the duration of a period. Further observations may be necessary to
conclusively rule out the presence of planets around CQVs.
